\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage{amssymb} % For \checkmark

% Setup for code listings (Safe ASCII version)
\lstset{
    basicstyle=\ttfamily\small,
    breaklines=true,
    frame=single,
    backgroundcolor=\color{gray!5},
    columns=fullflexible,
    keepspaces=true
}

\title{Technical Handover Document: GG-Bracket}
\author{Marc Dylan Myles C. Pilapil}
\date{April 2026}

\begin{document}

\maketitle

\section{Project Overview}
\textbf{GG-Bracket} is a full-stack tournament management system designed with Role-Based Access Control (RBAC). The platform facilitates two distinct user experiences:
\begin{itemize}
    \item \textbf{Admins:} Authorized personnel capable of CRUD operations on teams and match scores.
    \item \textbf{Viewers:} Public users with read-only access to standings and the visual bracket.
\end{itemize}

\section{System Architecture}
The system utilizes a 3-tier architecture to decouple the presentation layer from the data persistence layer.

\begin{table}[h!]
\centering
\begin{tabular}{@{}lll@{}}
\toprule
\textbf{Layer} & \textbf{Technology} & \textbf{Responsibility} \\ \midrule
Frontend & React + Chakra UI v3 & Responsive UI \& State Management \\
Backend & Node.js + Express & API Routing \& JWT Authentication \\
Database & PostgreSQL 18 & Persistent Relational Storage \\ \bottomrule
\end{tabular}
\caption{Technology Stack Breakdown}
\end{table}

\newpage % Force a fresh start if the previous page was getting crowded
\begin{minipage}{\textwidth}
\section{Project Skeleton}
% Using standard ASCII |, -, and + for the tree
\begin{lstlisting}
GG-Bracket/
|-- client/                # React Frontend
|   |-- src/
|   |   |-- api/           # Backend communication
|   |   |-- context/       # Auth & Role state
|   |   |-- features/      # Tournament & Bracket logic
|   |   `-- App.tsx        # Main routing
|-- server/                # Node.js Backend
|   |-- config/            # DB Connection (db.js)
|   |-- controllers/       # Auth & Match logic
|   |-- middleware/        # JWT & Admin verification
|   |-- routes/            # API Endpoints
|   `-- index.js           # Entry point
`-- .env                   # Environment secrets
\end{lstlisting}
\end{minipage}

\section{Database Schema}
The relational schema ensures data integrity using primary and foreign keys.
\begin{itemize}
    \item \textbf{users:} Contains username, email, password\_hash, and role.
    \item \textbf{teams:} Contains team metadata and logo\_url.
    \item \textbf{matches:} Tracks scores, rounds, and references the teams table.
\end{itemize}

\section{Current Development Status}
\begin{itemize}
    \item \textbf{UI/UX:} Done $\checkmark$
    \item \textbf{Database:} Done $\checkmark$
    \item \textbf{Auth Logic:} In Progress
\end{itemize}

\end{document}